### 2022-04-14 paper3.tex
copyedits, add desc stat table

\hypertarget{paper-3}{%
\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}

\hypertarget{abstract-1}{%
\section{Abstract}\label{abstract-1}}

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health
recommendations to mitigate the COVID-19 pandemic. Using theories like
associative diffusion and the integrated theoretical framework of norms, I test
models of behavioral adaption to public health recommendations and patterns of
complex contagion (the need for repeated exposures to a something novel for it
to diffuse) using linear mixed effects models. These models show that complex
contagion is a valid framework for the social contagion of new norms during
COVID-19. Importantly, I find a novel moderating effect of signal discordance,
the contextual diversity of signals received by an ego. If there is diversity in
the information received by an ego, contagion is less likely to occur. This
paper shows that the contagion process cannot be not fully understood without
looking at the context of each exposure to a contagion within the range of
contagions one experiences.

@@

This article researches the formation of social norms governing health behaviors
in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of
complex contagion, associative diffusion and the integrated theoretical
framework of norms, I test how these health behaviors are outcomes of contagion
and discordance of signals, as well as other factors affecting associations like
religious and political conservatism, attention to television media sources, and
online norms as measured by information-search behaviors. Before outlining my
central hypotheses, I offer an overview of the current state of the social
contagion literature. After that, I will outline how I compiled this unique
longitudinal data set from Google, the CDC, Facebook and other sources and how I
define and calculate signal and discordance, two key independent variables for
this paper. To model stay-at-home and vaccination rates, I use linear mixed
effects models with random effects as a longitudinal model of contagion. After
interpreting the results of the models, I discuss the implications of these
findings for the sociological understanding of social contagion and the
formation of social norms.

@@

Individuals engage with each other and their distributive ties to create
community contexts where norms, beliefs, and values circulate. These clusters of
interaction are called social networks, and if ``each person continues to
interact primarily with others nearby in space, the forces of conformity will be
strongest locally, leading to the emergence of clusters of people sharing
similar behavior'' \citep{kitts_shi18}. This community interaction ultimately
leads to converged communities of belief structures with variations in how much
they diverge from the norm \citep{cullumCulturalEvolutionInterpersonal2007,
lataneExperimentalEvidenceDynamic1996, okadaStructureCulturalRejection2017}.

@@

Most of the diffusion literature does not focus on establishment of new norms
but the adoption of culture and specific deviant behaviors \citep[see][for an
exception]{centolaSpontaneousEmergenceConventions2015}.
\citet{dellapostaWhyLiberalsDrink2015} outline how the spread of culture and
behavior is tied to network autocorrelation, or ``the tendency for people to
resemble their network neighbors.'' They show that the distance between to
agents in sociocultural space can determine the likelihood of the adoption of a
new behavior. Like \citet{axelrodDisseminationCultureModel1997}, this outlines
how the local convergence of close network actors becomes amplified and can lead
to global polarization between groups.

@@

\citep{centolaComplexContagionsWeakness2007} theorize that simple contagions are
not enough to spread behavioral change. Simple contagions are those in which
only one point of contact is needed to receive contagion, like with infectious
disease or to learn simple bits of information. Centola and Macy
\citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution was the
theorizing of complex contagions, those that require ``independent affirmation
or reinforcement from multiple sources'' (p. 703) and is not based on the number
of exposures but the number of sources of exposure. In the case of behavioral
contagion, this means that the behavior must be reinforced through witnessing
multiple alters perform this behavior before contagion can take effect.

@@

\begin{hyp2}[H\ref{hyp:direction}] \label{hyp:direction}
Increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
\end{hyp2}

To make the contagion more complex, different sources of exposure
(county-alters) adhere to CDC recommendations to stay-at-home at differing
rates. Whereas one county-alter may be greatly increasing its time in residence,
another may have made little change. When the majority of alters is in
concordance with each other, the signal to the ego is reinforced and more
impactful on the ego. When these signals are mixed with high variance from
different sources, agreement is low and makes the behavioral change less likely.
For this paper, I theorize that a new concept of `discordance' must be
considered as impacting complex contagion. discordance is the variance of
signals received by an alter; high discordance prevents reinforcement while low
discordance (concordance) enables complex contagion. Instead of adopting a
`majority' rules attitude, this means that the more discordance perceived by an
ego, the less likely the alters will have any effect on the ego. I theorize that
the behavior of a county-alter will be positively correlated with the behavior
of another county-ego if the county-ego receives highly discordant signals, as
seen in Figure \ref{fig:dag}.

@@

\hypertarget{associative-diffusion}{%
\subsection{Associative Diffusion}\label{associative-diffusion}}

@@

\input{tables/paper3/google-desc-table}

@@

My first dependent variable aims to operationalize behavioral norms as
stay-at-home rates with data from Google \citep{google2020}. While the Google
COVID-19 Community Mobility Reports include multiple measures of mobility based
on location and activity information, the change in time spent in residence most
closely aligns to an operationalization of an obedience to CDC and governor
orders, a new and emerging norm in 2020. The change in time spent in residence
variable represents percent change of time spent from Google Location History
within geographic areas that Google has designated as a residential area. These
data are aggregated to the county-level based on anonymized sets of data from
users who have turned on the Location History setting, which is off by default.
This means our sample is possibly skewed to people in the United States a) with
a mobile phone, b) with a Google account, and c) with knowledge of how to
synchronize their location history. Google has not made it clear whether there
are any weights in place to correct for these potential biases. Google
calculates the relative change in mobility in comparison to the median value of
movement in the area for the same the corresponding day of the week, during the
5-week period Jan 3--Feb 6, 2020. As Google did not provide data on certain US
counties if they did not have sufficient statistically significant levels of
data, my final county sample is \emph{n} = 1375 (compared to the total
population of 3,107 US counties). Particular areas that are excluded in this
analysis include all counties in Alaska and DC, and over half of the counties in
North Dakota, South Dakota. A full list of excluded counties available upon
request. These data are longitudinal measures calculated by creating a moving
average of stay-at-home rates for each county (rolling window width = 7 days)
and then sampling every Monday in the sample for 44 measures from March 02, 2020
through December 28, 2020.

\hypertarget{covid-vaccination-uptake}{%
\subsection{COVID vaccination uptake}\label{covid-vaccination-uptake}}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-1}}
\caption{Vaccination Rates over Time}\label{fig:plot-vacc}
\end{figure}

@@

\hypertarget{independent-variables-1}{%
\subsection{Independent Variables}\label{independent-variables-1}}

\hypertarget{network-signal}{%
\subsubsection{Network Signal}\label{network-signal}}

@@

\hypertarget{signal-discordance}{%
\subsubsection{Signal Discordance}\label{signal-discordance}}

@@

Figures \ref{fig:assortativity-vacc} and \ref{fig:discordancenetwork} provide a
visualization of both network signal and signal discordance for April 26, 2021
for 7 selected counties.\footnote{Figures in this paper were all created using
ggplot2 \citep{wickham_etal, wickham11}, patchwork \citep{pedersen20}, and
ggridges \citep{ggridges}} While a county like Lake County, Ohio has low
discordance meaning the signal of vaccination rate is reinforced, Navajo County,
Arizona receives very diverse signals from their county-alters, negating any
contagion effects. Figure \ref{fig:discordancenetwork} explicitly outline how
the weights and signals are calculated for an ego with only 5 alters.

@@

\begin{figure}
\begin{center}\includegraphics[width=0.5\linewidth,]{figs/paper3/discordancenetwork-1.pdf} 
  \begin{equation}
    w = \begin{bmatrix}0.0000015\\0.0000023\\0.0000527\\0.0000966\\0.0001119\end{bmatrix},  
    x = \begin{bmatrix}29.9\\20.4\\27.7\\24.6\\24.3\end{bmatrix} \longrightarrow
    \begin{matrix} \bar{x}*, signal = 25.083\\ s*, discordance = 1.41 \end{matrix} 
  \end{equation}
  \caption{How Network Signal and Discordance are Calculated, Mathematical Example}
  \label{fig:discordancenetwork}
  \end{center}
\end{figure}

\hypertarget{COVID-19-case-rates}{%
\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}

@@

\hypertarget{pillars-of-convervatism}{%
\subsubsection{Pillars of Convervatism}\label{pillars-of-convervatism}}

Research has shown that stay-at-home rates and other pandemic health behaviors
are related to various `pillars of conservatism'
\citep{gonzalez_etal21,hillBloodChristCompels2020,hillLoveThyAged2021,
hillNastiestQuestion}. Namely, research shows that politically conservative
indicators, such as Republican political leadership, conservative Protestantism
and consumption of right-wing media are related to higher rates of movement and
lower rates of mask usage. Based on these findings, this article controls for
these factors in the following ways: to measure Republican political leadership,
I include percentage of votes for Donald Trump in the previous presidential
election; for the 2020 study, I use the 2016 results and for the 2021 study, I
use the 2020 results to infer proper time ordering. Second, to measure
conservative Protestantism, I employ the county's percentage of evangelical
Christians. These county-level data were collected through the 2010 U.S.
Religion Census: Religious Congregations and Membership Study
\citep{grammich_etal18}. Finally, right-wing media consumption is assessed using
Google Search Trends to capture ``Fox News'' searches over the study period
across individual designated media markets areas (DMAs). I use this measure to
indicate active interest in and attention toward Fox News. Google Search Trends
have been validated for use in a range of research contexts and for use with
survey data, voting data, and ecological data
\citep{bailPrestigeProximityPrejudice2019, reyesUsingInternetSearch2018,
scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014,
swearingenGoogleInsightsSenate2014}.

\hypertarget{demographics}{%
\subsubsection{Demographics}\label{demographics}}

@@

\hypertarget{analysis-and-results}{%
\section{Analysis and Results}\label{analysis-and-results}}

My analytic strategy proceeds in four steps. In Tables
\ref{tab:google-desc-table} (Stay-at-Home) and \ref{tab:vacc-desc-table}
(Vaccination Uptake), I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations across the two cases.
Then, in Tables \ref{tab:google-tab} - \ref{tab:vacc-tab}, I fit a series of
three linear mixed effects regression models using the nlme package in R
\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates
and Vaccination rates. Linear mixed effects models are a form of hierarchical
linear models that contain both random and fixed effects. These models treat the
dependent variables as continuous. The following strategies I will outline are
identical for both case studies. Models 1 through 3 address hypotheses
\ref{hyp:infection} through \ref{hyp:discordance} respectively. Each model
utilizes normalized independent variables, i.e. variables that have been
centered and scaled to have a mean of 0 and standard deviation 1. The first
model is a baseline linear mixed effects model that employs all basic controls
to predict the dependent variable, allowing both time-varying and county-level
variables to predict the outcome. All variables have fixed effects, meaning that
the county-level exogenous effects are controlled for when estimating the
coefficient. In addition, models are specified with a random intercept per
county. The lme models are set with a autoregressive correlation structure
(\texttt{correlation\ =\ corAR1()}) to control for temporally autocorrelated
error structures; models are also optimized using Nelder--Mead, quasi-Newton and
conjugate-gradient algorithms for box-constrained optimization and simulated
annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}). This first model
will address Hypothesis \ref{hyp:infection}. To test Hypothesis
\ref{hyp:direction}, I estimate model 2 which builds on model 1 by first
introducing vaccination signal. Because the signal varies by week, I estimate
this model with an interaction between week and signal. And finally, because
signal may have divergent effects across counties, I set a random effect for
signal nested by county. A visual representation of this interaction can be seen
in Figures \ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
elaborates on the previous model by introducing both a fixed effect for signal
discordance and an interaction term between signal and discordance. Figures
\ref{fig:plot-google-h3} and \ref{fig:plot-vacc-h3} depict just how signal and
discordance interact across these two cases.

\hypertarget{stay-at-home-rate-results}{%
\subsection{Stay-at-Home Rate results}\label{stay-at-home-rate-results}}

@@

Model 3 then adds the concept of Signal Discordance to investigate Hypothesis
\ref{hyp:discordance}, that the effect of signal direction on stay-at-home rates
will be moderated by a diversity in signals (\emph{discordance}). Many of the
controls remain consistent throughout the models, with the exception of `Social
Distancing' Trend whose effect has been completely mediated by the inclusion of
signal discordance. Importantly, signal discordance has a negative effect on
stay-at-home rates, where every one standard deviation increase in discordance
lowers stay-at-home rates by -0.101 (\emph{p} \textless{} 0.001). The
interaction between signal and signal discordance have a coefficient of a
similar magnitude, with every one standard deviation increase in discordance and
signal resulting in -0.092 lower rates of time spent in residence, indicating
moderation. Figure \ref{fig:plot-google-h3} illustrates the moderating effect
that signal discordance has on signal. Under high discordance, the social
influence effect is almost completely moderated because there is no clear story
or norm forming. However, under low discordance, the signal is condensed,
allowing for social influence to have an effect. Explicitly, if a county is
receiving a wide array of low and high signals, their stay-at-home rates won't
be affected by social contagion. When a signal is concentrated or in agreement,
the theoretical effect of movement signaling on the ego are the strongest. With
this, I am able to reject the null hypothesis of no relationship for Hypothesis
\ref{hyp:discordance} and find that the effect of signal direction on time spent
in residence is moderated by diversity in signals.

\hypertarget{vaccination-rate-results}{%
\subsection{Vaccination Rate results}\label{vaccination-rate-results}}

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses Hypothesis \ref{hyp:infection}, that
relatively higher local rates of infection will lead to increased vaccination
uptake. In this first model, we see various controls impacting vaccination
rates. For instance, when controlling for everything else, higher income areas
lead to higher vaccination uptake. On the other hand, counties with higher
unemployment and higher votes for Donald J. Trump in the 2020 election are
associated with lower vaccination rates. Interestingly, counties that search for
Fox News are more likely to have higher vaccination rates while those performing
Google searches for information about the vaccine are likely to have lower rates
of vaccination. The test of Hypothesis \ref{hyp:infection} also returns
surprising results: every 1 standard deviation increase in county COVID-19 case
rates is expected to yield a -0.008 decrease in vaccination rates. This may be
due to time ordering or reverse causality, where individuals in counties who
have higher rates of vaccination are less likely to take tests to COVID-19
infections because of the higher likelihood of asymptomaticity. However, it is
important to note that the Case Rate variable actually becomes distorted with
the addition of Vaccination Signal and Vaccination Discordance in models 2 and
3. Distortion occurs when the direction of a focal relationship reverses sign
once a third (distorter) variable is controlled, in this case, those related to
signal. Therefore, the results of Hypothesis \ref{hyp:infection} are quite
inconclusive.

@@

\hypertarget{discussion-and-conclusion}{%
\section{Discussion and Conclusion}\label{discussion-and-conclusion}}

@@

This study is sensitive to aggregation error and sampling error derived from the
multiple big-data sources \citep{facebook20, google2020}. The aggregation errors
are potentially linked to the assumption that the average stay-at-home behavior
of a county is a good representation of the diversity in behaviors within that
county. If stay-at-home rates are normally distributed, this is a correct
assumption to make; however, little is known about each county's underlying
distribution of behaviors that lead to the aggregate measures.

Regardless of limitations, this article is a unique and compelling contribution
to the academic study of social contagion and social norms. First, this article
demonstrates that it is possible to link, at least at a community level,
information search by individuals, social relationships, and observed health
behaviors without being limited to self-report measures of perceptions,
attitudes, or intentions about behavior. Sociological research has long debated
about the agency of individuals and the social and institutional structure in
which individuals are immersed. In this study, I aggregate beyond the individual
case to explore overall patterns of movement and vaccination which summarizes
individual agency of health behaviors together.

>>>>

\hypertarget{paper-3}{\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}

\hypertarget{abstract-1}{\section{Abstract}\label{abstract-1}}

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health
recommendations to mitigate the COVID-19 pandemic. Using theories like
associative diffusion and the integrated theoretical framework of norms, I test
models of behavioral adaption to public health recommendations and patterns of
complex contagion (the need for repeated exposures to something novel for it
to diffuse) using linear mixed effects models. These models show that complex
contagion is a valid framework for the social contagion of new norms during
COVID-19. Importantly, I find a novel moderating effect of signal discordance,
the contextual diversity of signals received by an ego. If there is diversity in
the information received by an ego, contagion is less likely to occur. This
paper shows that the contagion process cannot be fully understood without
looking at the context of each exposure to a contagion within the range of
contagions one experiences.

@@

This article researches the formation of social norms governing health behaviors
in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of
complex contagion, associative diffusion and the integrated theoretical
framework of norms, I test how these health behaviors are outcomes of contagion
and discordance of signals, as well as other factors affecting associations like
religious and political conservatism, attention to television media sources, and
online norms as measured by information-search behaviors.

Before outlining my
central hypotheses, I offer an overview of the current state of the social
contagion literature. After that, I will outline how I compiled this unique
longitudinal data set from Google, the CDC, Facebook and other sources and how I
define and calculate signal and discordance, two key independent variables for
this paper. To model stay-at-home and vaccination rates, I use linear mixed
effects models with random effects as a longitudinal model of contagion. After
interpreting the results of the models, I discuss the implications of these
findings for the sociological understanding of social contagion and the
formation of social norms.

@@

Individuals engage with each other and their distributed ties to create
community contexts where norms, beliefs, and values circulate. These clusters of
interaction are called social networks, and if ``each person continues to
interact primarily with others nearby in space, the forces of conformity will be
strongest locally, leading to the emergence of clusters of people sharing
similar behavior'' \citep{kitts_shi18}. This community interaction ultimately
leads to converged communities of belief structures with variations in how much
they diverge from the norm \citep{cullumCulturalEvolutionInterpersonal2007,
lataneExperimentalEvidenceDynamic1996, okadaStructureCulturalRejection2017}.

@@

Most of the diffusion literature does not focus on establishment of new norms
but the adoption of culture and specific deviant behaviors \citep[see][for an
exception]{centolaSpontaneousEmergenceConventions2015}.
\citet{dellapostaWhyLiberalsDrink2015} outline how the spread of culture and
behavior is tied to network autocorrelation, or ``the tendency for people to
resemble their network neighbors.'' They show that the distance between two
agents in sociocultural space can determine the likelihood of the adoption of a
new behavior. Like \citet{axelrodDisseminationCultureModel1997}, this outlines
how the local convergence of close network actors becomes amplified and can lead
to global polarization between groups.

@@

\citet{centolaComplexContagionsWeakness2007} theorize that simple contagions are
not enough to spread behavioral change. Simple contagions are those in which
only one point of contact is needed to receive contagion, like with infectious
disease or to learn simple bits of information. Centola and Macy
\citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution was the
theorizing of complex contagions, those that require ``independent affirmation
or reinforcement from multiple sources'' (p. 703) and is not based on the number
of exposures but the number of sources of exposure. In the case of behavioral
contagion, this means that the behavior must be reinforced through witnessing
multiple alters perform this behavior before contagion can take effect.

@@

\begin{hyp2}[H\ref{hyp:direction}] \label{hyp:direction}
Increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
\end{hyp2}
% TODO I think I ``get'' this, but could you define ``ego county''? Also, why not just look at the effect of alter's behavior on ego's behavior (why does the county come into the framework)? Do you mean {the subset of ego's alters who live in the same county as ego}?

To make the contagion more complex, different sources of exposure
(county-alters) adhere to CDC recommendations to stay-at-home at differing
rates. Whereas one county-alter may be greatly increasing its time in residence,
another may have made little change. When the majority of alters is in
concordance with each other, the signal to the ego is reinforced and more
impactful on the ego. When these signals are mixed with high variance from
different sources, agreement is low and makes the behavioral change less likely.
For this paper, I theorize that a new concept of `discordance' must be
considered as impacting complex contagion. Discordance is the variance of
signals received by an alter; high discordance prevents reinforcement while low
discordance (concordance) enables complex contagion. Instead of adopting a
`majority' rules attitude, this means that the more discordance perceived by an
ego, the less likely the alters will have any effect on the ego. I theorize that
the behavior of a county-alter will be correlated with the behavior
of another county-ego if the county-ego receives highly discordant signals, as
seen in Figure \ref{fig:dag}.

@@

\hypertarget{associative-diffusion}{\subsection{Associative Diffusion}\label{associative-diffusion}}

@@

\input{tables/paper3/google-desc-table}
%TODO define normalization, make sure its mentioned in the methods section

@@

My first dependent variable aims to operationalize behavioral norms as
stay-at-home rates with data from Google \citep{google2020}. While the Google
COVID-19 Community Mobility Reports include multiple measures of mobility based
on location and activity information, the change in time spent in residence most
closely aligns to an operationalization of an obedience to CDC and governor
orders, a new and emerging norm in 2020. The change in time spent in residence
variable represents percent change of time spent from Google Location History
within geographic areas that Google has designated as a residential area. These
data are aggregated to the county-level based on anonymized sets of data from
users who have turned on the Location History setting, which is off by default.
This means our sample is possibly skewed to people in the United States a) with
a mobile phone, b) with a Google account, and c) with knowledge of how to
synchronize their location history. Google has not made it clear whether there
are any weights in place to correct for these potential biases. Google
calculates the relative change in mobility in comparison to the median value of
movement in the area for the same corresponding day of the week, during the
5-week period Jan 3--Feb 6, 2020. As Google did not provide data on certain US
counties if they did not have sufficient statistically significant levels of
data, my final county sample is \emph{n} = 1375 (compared to the total
population of 3,107 US counties). Particular areas that are excluded in this
analysis include all counties in Alaska and DC, and over half of the counties in
North Dakota, South Dakota. A full list of excluded counties available upon
request. These data are longitudinal measures calculated by creating a moving
average of stay-at-home rates for each county (rolling window width = 7 days)
and then sampling every Monday in the sample for 44 measures from March 02, 2020
through December 28, 2020.

\hypertarget{covid-vaccination-uptake}{\subsection{COVID vaccination uptake}\label{covid-vaccination-uptake}}

@@

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-1}}
\caption{Vaccination Rates over Time}\label{fig:plot-vacc}
\end{figure}
% TODO add which counties rose to 100% vaccination

@@

\hypertarget{independent-variables-1}{\subsection{Independent Variables}\label{independent-variables-1}}

\hypertarget{network-signal}{\subsubsection{Network Signal}\label{network-signal}}

@@

\hypertarget{signal-discordance}{\subsubsection{Signal Discordance}\label{signal-discordance}}

@@

Figures \ref{fig:assortativity-vacc} and \ref{fig:discordancenetwork} provide a
visualization of both network signal and signal discordance for April 26, 2021
for 7 selected counties.\footnote{Figures in this paper were all created using
ggplot2 \citep{wickham_etal, wickham11}, patchwork \citep{pedersen20}, and
ggridges \citep{ggridges}} While a county like Lake County, Ohio has low
discordance meaning the signal of vaccination rate is reinforced, Navajo County,
Arizona receives very diverse signals from their county-alters, negating any
contagion effects. Figure \ref{fig:discordancenetwork} explicitly outline how
the weights and signals are calculated for an ego with only 5 alters.
% TODO Navajo County, AZ, is probably a good one to talk about. Suppose it's composed of Native and non-Native communities, which are not in much communication with each other. Each (Native and non-Native) might have connections to different sets of alter counties. In brief: There could be a lot of homogeneity among non-Natives and a lot of homogeneity among Natives, but both might be masked by taking county as the unit. Thoughts? the assumption of homogeneity within county  (my comment on p. 120) should be stated clearly.

@@

\begin{figure}
\begin{center}\includegraphics[width=0.5\linewidth,]{figs/paper3/discordancenetwork-1.pdf} 
  \begin{equation}
    w = \begin{bmatrix}0.0000015\\0.0000023\\0.0000527\\0.0000966\\0.0001119\end{bmatrix},  
    x = \begin{bmatrix}29.9\\20.4\\27.7\\24.6\\24.3\end{bmatrix} \longrightarrow
    \begin{matrix} \bar{x}*, signal = 25.083\\ s*, discordance = 1.423 \end{matrix} 
  \end{equation}
  \caption{How Network Signal and Discordance are Calculated, Mathematical Example}
  \label{fig:discordancenetwork}
  \end{center}
\end{figure}

\hypertarget{COVID-19-case-rates}{\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}

@@

\hypertarget{pillars-of-convervatism}{\subsubsection{Pillars of Convervatism}\label{pillars-of-convervatism}}

Research has shown that stay-at-home rates and other pandemic health behaviors
are related to various `pillars of conservatism'
\citep{gonzalez_etal21,hillBloodChristCompels2020,hillLoveThyAged2021,
hillNastiestQuestion}. Namely, research shows that politically conservative
indicators, such as Republican political leadership, conservative Protestantism
and consumption of right-wing media are related to higher rates of movement and
lower rates of mask usage. Based on these findings, this article controls for
these factors in the following ways: to measure Republican political leadership,
I include percentage of votes for Donald Trump in the previous presidential
election; for the 2020 study, I use the 2016 results and for the 2021 study, I
use the 2020 results to infer proper time ordering. Second, to measure
conservative Protestantism, I employ the county's percentage of evangelical
Christians. These county-level data were collected through the 2010 U.S.
Religion Census: Religious Congregations and Membership Study
\citep{grammich_etal18}. Finally, right-wing media consumption is assessed using
Google Search Trends to capture ``Fox News'' searches over the study period
across individual designated media markets areas (DMAs). I use this measure to
indicate active interest in and attention toward Fox News. While Google Search Trends
have been validated for use in a range of research contexts and for use with
survey data, voting data, and ecological data
\citep{bailPrestigeProximityPrejudice2019, reyesUsingInternetSearch2018,
scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014,
swearingenGoogleInsightsSenate2014}, I provide a caution for these uses in 
\hyperlink{paper-1}{Appendix A} and suggest these measures should only be used to measure attention.

\hypertarget{demographics}{\subsubsection{Demographics}\label{demographics}}

@@

\hypertarget{analysis-and-results}{\section{Analysis and Results}\label{analysis-and-results}}

My analytic strategy proceeds in four steps. In Tables
\ref{tab:google-desc-table} (Stay-at-Home) and \ref{tab:vacc-desc-table}
(Vaccination Uptake), I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations across the two cases.
Then, in Tables \ref{tab:google-tab} - \ref{tab:vacc-tab}, I fit a series of
three linear mixed effects regression models using the nlme package in R
\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates
and Vaccination rates. Linear mixed effects models are a form of hierarchical
linear models that contain both random and fixed effects. These models treat the
dependent variables as continuous. The following strategies I will outline are
identical for both case studies. Models 1 through 3 address hypotheses
\ref{hyp:infection} through \ref{hyp:discordance} respectively. Each model
utilizes normalized independent variables, i.e.\ variables that have been
centered and scaled to have a mean of 0 and standard deviation 1. The first
model is a baseline linear mixed effects model that employs all basic controls
to predict the dependent variable, allowing both time-varying and county-level
variables to predict the outcome. All variables have fixed effects, meaning that
the county-level exogenous effects are controlled for when estimating the
coefficient. In addition, models are specified with a random intercept per
county. The lme models are set with a autoregressive correlation structure
(\texttt{correlation\ =\ corAR1()}) to control for temporally autocorrelated
error structures; models are also optimized using Nelder--Mead, quasi--Newton and
conjugate--gradient algorithms for box-constrained optimization and simulated
annealing (\texttt{control\ =\ lmeControl(opt\ =\ ``optim'')}). This first model
will address Hypothesis \ref{hyp:infection}. To test Hypothesis
\ref{hyp:direction}, I estimate model 2 which builds on model 1 by first
introducing vaccination signal. Because the signal varies by week, I estimate
this model with an interaction between week and signal. And finally, because
signal may have divergent effects across counties, I set a random effect for
signal nested by county. A visual representation of this interaction can be seen
in Figures \ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
elaborates on the previous model by introducing both a fixed effect for signal
discordance and an interaction term between signal and discordance. Figures
\ref{fig:plot-google-h3} and \ref{fig:plot-vacc-h3} depict just how signal and
discordance interact across these two cases.

\hypertarget{stay-at-home-rate-results}{
\subsection{Stay-at-Home Rate results}\label{stay-at-home-rate-results}}

@@

Model 3 then adds the concept of Signal Discordance to investigate Hypothesis
\ref{hyp:discordance}, that the effect of signal direction on stay-at-home rates
will be moderated by a diversity in signals (\emph{discordance}). Many of the
controls remain consistent throughout the models, with the exception of `Social
Distancing' Trend whose effect has been completely mediated by the inclusion of
signal discordance. Importantly, signal discordance has a negative effect on
stay-at-home rates, where every one standard deviation increase in discordance
lowers stay-at-home rates by -0.101 (\emph{p} \textless{} 0.001). The
interaction between signal and signal discordance have a coefficient of a
similar magnitude, with every one standard deviation increase in discordance and
signal resulting in -0.092 lower rates of time spent in residence, indicating
moderation. Figure \ref{fig:plot-google-h3} illustrates the moderating effect
that signal discordance has on signal. Under high discordance, the social
influence effect is almost completely moderated because there is no clear story
or norm forming. However, under low discordance, the signal is condensed,
allowing for social influence to have an effect. Explicitly, if a county is
receiving a wide array of low and high signals, their stay-at-home rates won't
be affected on average by social contagion. When a signal is concentrated or in agreement,
the theoretical effect of movement signaling on the ego are the strongest. With
this, I am able to reject the null hypothesis of no relationship for Hypothesis
\ref{hyp:discordance} and find that the effect of signal direction on time spent
in residence is moderated by diversity in signals.

\hypertarget{vaccination-rate-results}{\subsection{Vaccination Rate results}\label{vaccination-rate-results}}

@@

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data \citep{finch_etal14}. Table
\ref{tab:vacc-tab} Model 1 addresses Hypothesis \ref{hyp:infection}, that
relatively higher local rates of infection will lead to increased vaccination
uptake. In this first model, we see various controls impacting vaccination
rates. For instance, when controlling for everything else, higher income areas
lead to higher vaccination uptake. On the other hand, counties with higher
unemployment and higher votes for Donald J. Trump in the 2020 election are
associated with lower vaccination rates. Interestingly, counties that search for
Fox News are more likely to have higher vaccination rates while those performing
Google searches for information about the vaccine are likely to have lower rates
of vaccination. 
% TODO On the Fox News result--Interesting. In hindsight, this too may have to do with inhomogeneities within counties, e.g., maybe it's the conservatives in liberal counties that tune in avidly to Fox News.
The test of Hypothesis \ref{hyp:infection} also returns
surprising results: every 1 standard deviation increase in county COVID-19 case
rates is expected to yield a -0.008 decrease in vaccination rates. This may be
due to time ordering or reverse causality, where individuals in counties who
have higher rates of vaccination are less likely to take tests to COVID-19
infections because of the higher likelihood of asymptomaticity. However, it is
important to note that the Case Rate variable actually becomes distorted with
the addition of Vaccination Signal and Vaccination Discordance in models 2 and
3. Distortion occurs when the direction of a focal relationship reverses sign
once a third (distorter) variable is controlled, in this case, those related to
signal. Therefore, the results of Hypothesis \ref{hyp:infection} are quite
inconclusive.
% TODO Those who perform Google searches for vaccine info are likely to have lower vaccination rates --> Maybe they are searching for info about why the vaccine is bad !!

% TODO An increase in covid cases yields a decrease in vaccination rates. -- Well, the association would be like this if low vaccination rates lead to more covid cases.

@@

\hypertarget{discussion-and-conclusion}{\section{Discussion and Conclusion}\label{discussion-and-conclusion}}

@@

This study is sensitive to aggregation error and sampling error derived from the
multiple big-data sources \citep{facebook20, google2020}. The aggregation errors
are potentially linked to the assumption that the average stay-at-home behavior
of a county is a good representation of the diversity in behaviors within that
county. If stay-at-home rates are normally distributed, this is a correct
assumption to make; however, little is known about each county's underlying
distribution of behaviors that lead to the aggregate measures.
% TODO As perhaps illustrated hypothetically in my comment on p. 120

Despite limitations, this article is a unique and compelling contribution
to the academic study of social contagion and social norms. First, this article
demonstrates that it is possible to link, at least at a community level,
information search by individuals, social relationships, and observed health
behaviors without being limited to self-report measures of perceptions,
attitudes, or intentions about behavior. Sociological research has long debated
about the agency of individuals and the social and institutional structure in
which individuals are immersed. In this study, I aggregate beyond the individual
case to explore overall patterns of movement and vaccination which summarizes
individual agency of health behaviors together.
